Novel Sampling Using Stochastic Gradient Descent

### 2016-12-05 poster/main.tex
poster initial

\usepackage[scale=1.24]{beamerposter} % Use the beamerposter package for laying out the poster

@@

\newlength{\sepwid}
\newlength{\onecolwid}
\newlength{\twocolwid}
\newlength{\threecolwid}
\setlength{\paperwidth}{48in} % A0 width: 46.8in
\setlength{\paperheight}{36in} % A0 height: 33.1in
\setlength{\sepwid}{0.024\paperwidth} % Separation width (white space) between columns
% \setlength{\onecolwid}{0.22\paperwidth} % Width of one column
% \setlength{\twocolwid}{0.464\paperwidth} % Width of two columns
% \setlength{\threecolwid}{0.708\paperwidth} % Width of three columns
\setlength{\onecolwid}{0.3013\paperwidth} % Width of one column
\setlength{\twocolwid}{0.6026\paperwidth} % Width of two columns
\setlength{\threecolwid}{0.904\paperwidth} % Width of three columns
\setlength{\topmargin}{-0.5in} % Reduce the top margin size
%-----------------------------------------------------------

@@

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------

@@

\begin{algorithm}[H]
{\small
Given data $X_1,\ldots, X_n$, model $p(X|\theta)$, sample size $K$
\begin{algorithmic}\caption{SGD based sampling}\label{Alg:SGD_Sampling}
\STATE {\bf Initialize} $ \theta^0$, $t \gets 0$;
\WHILE{stopping criterion not satisfied}
\STATE draw $K$ iid samples with replacement from $1,\ldots, n$, denoted $\eta_1,\ldots, \eta_K$.
\STATE calculate the mean $a^t$ and the variance $v^t$ of $(\nabla\log p(X_{\eta_i}|\theta^t))_{i=1}^K$.
\STATE set the stepsize $\alpha^t \gets K^{-1} v^t$
\STATE
$\theta^{t+1} \gets \theta^t + \alpha^ta^t$;
\STATE $t\gets t+1$;
\ENDWHILE
\STATE return $\theta^k$.
\end{algorithmic}}
\end{algorithm}

@@

\begin{figure}
\includegraphics[width=0.8\linewidth]{placeholder.jpg}
\caption{Figure caption}
\end{figure}

@@

The following materials were required to complete the research:

\begin{itemize}
\item Curabitur pellentesque dignissim
\item Eu facilisis est tempus quis
\item Duis porta consequat lorem
\item Eu facilisis est tempus quis
\end{itemize}

The materials were prepared according to the steps outlined below:

\begin{enumerate}
\item Curabitur pellentesque dignissim
\item Eu facilisis est tempus quis
\item Duis porta consequat lorem
\item Curabitur pellentesque dignissim
\end{enumerate}

@@

@@

\begin{figure}
\includegraphics[width=0.8\linewidth]{placeholder.jpg}
\caption{Figure caption}
\end{figure}

>>>>

% \usepackage[scale=1.24]{beamerposter} % Use the beamerposter package for laying out the poster
\usepackage[scale=0.8]{beamerposter}

@@

\newlength{\sepwid}
\newlength{\onecolwid}
\newlength{\twocolwid}
\newlength{\threecolwid}
% \setlength{\paperwidth}{48in} % A0 width: 46.8in
% \setlength{\paperheight}{36in} % A0 height: 33.1in
\setlength{\paperwidth}{36in} % A0 width: 46.8in
\setlength{\paperheight}{24in} % A0 height: 33.1in
\setlength{\sepwid}{0.024\paperwidth} % Separation width (white space) between columns
% \setlength{\onecolwid}{0.22\paperwidth} % Width of one column
% \setlength{\twocolwid}{0.464\paperwidth} % Width of two columns
% \setlength{\threecolwid}{0.708\paperwidth} % Width of three columns
\setlength{\onecolwid}{0.3013\paperwidth} % Width of one column
\setlength{\twocolwid}{0.6026\paperwidth} % Width of two columns
\setlength{\threecolwid}{0.904\paperwidth} % Width of three columns
\setlength{\topmargin}{-0.5in} % Reduce the top margin size
%-----------------------------------------------------------

@@

\newcommand{\bx}{\mathbf{x}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\E}{\mathbb{E}}
\newcommand{\D}{\mathscr{D}}
\newcommand{\N}{\mathscr{N}}
\newcommand{\by}{\mathbf{y}}
\newcommand{\var}{\mathrm{var}}
\DeclareMathOperator*{\argmin}{\arg\!\min}

\newtheorem{conjecture}{Conjecture}
% \newtheorem{theorem}{Theorem}
\newtheorem{experiment}{Experiment}

% inline theorem
\makeatletter
\setbeamertemplate{theorem begin}
  {\usebeamercolor[fg]{thcolor}% for the heading
  {\bfseries\inserttheoremname~}%
  \ifx\inserttheoremaddition\@empty\else(\inserttheoremaddition)\ \fi%
  \hspace{.01em}\normalfont\usebeamercolor[fg]{thcolor}% for the body
  }
\setbeamertemplate{theorem end}{}
\makeatother
%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

@@

%----------------------------------------------------------------------------------------
%   MOTIVATION
%----------------------------------------------------------------------------------------

\begin{block}{Motivation}

\begin{itemize}
    \item aaa
\end{itemize}

%------------------------------------------------
%
%----------------------------------------------------------------------------------------
%	INTRODUCTION
%----------------------------------------------------------------------------------------

@@

\begin{algorithm}[H]
{\small
Given objective function $h(x)$, stepsize $\alpha$, noise level $\sigma^2$,
\begin{algorithmic}\caption{Stochastic gradient descent (oracle)}\label{Alg:SGD}
\STATE {\bf Initialize} $ \bx^0$ arbitrarily;
\WHILE{stopping criterion not satisfied}
\STATE draw $\epsilon^t$ from Gaussian distribution $\N(0, \sigma^2)$.
\STATE
$\bx^{k+1} \gets \bx^k - \alpha\nabla f(\bx^k) + \epsilon^t$;
\STATE $k\gets k+1$;
\ENDWHILE
\STATE return $\bx^k$.
\end{algorithmic}}
\end{algorithm}

@@

@@

\begin{conjecture}
For any $p(\bx)\in \D(\R^p)$, it is the stationary distribution of iterates in Algorithm 1 with parameter $(-\log p(\bx), \epsilon, 2\epsilon)$.
\end{conjecture}

@@

\begin{theorem}[Central limit theorem]
Let $K = \alpha^{-1} \var \log P(X_1|\theta^t)$,
\[
\sum_{i=1}^K (K^{-1}\nabla \log P(X_{\eta_i}|\theta^t) - \log P(\theta^t)) - (n^{-1} \sum_{i=1}^n \nabla \log P(X_i|\theta^t) - \log P(\theta^t)) \sim \N(0, \alpha).
\]
\end{theorem}

A toy example showing SGD works.

@@

\begin{figure}
\includegraphics[width=0.4\linewidth]{../figure/simulation2_empirical.png}
\includegraphics[width=0.4\linewidth]{../figure/simulation2_real.png}
\caption{Figure caption}
\end{figure}
